\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Wayne Havey Journal \#7\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Wayne R. Havey III}
\IEEEauthorblockA{\textit{PhD Student: Security Track} \\
\textit{UCCS}\\
Colorado Springs, CO \\
whavey@uccs.edu}
}

\maketitle

\section{Survey Paper Learning - 2nd Draft}
This week the focus has been finishing a second draft for the survey paper. Much of the time was spent writing the more discussion focused sections. I decided to keep the list of papers as its own section as I found it to be nicer to read as a distinct section. I also think I did it because it was much easier than trying to integrated the papers into the rest of the discussion.\\
I learned it wasnt difficult to write the discussion portions if I just made a different section for the high level categories of the taxonomy I am proposing. This made up most of the draft. The remaining sections were a little difficult to determine their placement in the paper. Most of them ended up before the first category discussion section. The conclusion was easy to write using the strategy of rewritting the abstract in different words.\\
I needed to spend more time working on diagrams. They take such a long time though and I spent so much on the main diagram that I think for this draft its ok that its the only one in the paper. The other diagrams I was planning to include are basically just sub classifications that can be inferred from the main taxonomy diagram anyway
\end{document}
